Assignment 3

### 2015-02-16 rmtw/a3/latex8.tex
Small changes to a few sections

\SubSection{Problem Statement}
The purpose of this paper is therefore to determine whether an organisation's development paradigm should be the basis for deciding which process and design changes to adopt.

%Maybe not this bit-----------------------------------------------------------
To explore this area, we focus on process and design practices that have been introduced at Ericsson EPG.
%Maybe not this bit-----------------------------------------------------------

>>>>

\SubSection{Problem Statement}
%big problem in industry implementing change
%could a reason for this be because they're trying to fit one thing onto something different. Focus on implementation rather than what the changes are
